---
title: "Package Setup"
author: "Jacob Peterson"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Install Starting packages
```{r}
renv::install('usethis')
renv::install('gitcreds')
```


## GITHUB_PAT
Make sure PAT is accessible in the package. Run `usethis::edit_r_profile('project')` to open up the project R profile and then add the following line so that the PAT is accessible to {remotes} and {renv} as a environmental variable (GITHUB_PAT). 
```{r}
#make sure to leave a blank line at the end of the file when you save it
Sys.setenv('GITHUB_PAT' = gitcreds::gitcreds_get()[['password']])

```


## Setup ROxygen
Delete the default NAMESPACE document  
Then run:
```{r}
renv::install('devtools')
devtools::document()
```



## Add packages to imports:
Adds the relevant lines to the package DESCTIPTION file:
```{r}
usethis::use_package('renv')
usethis::use_package('gitcreds')
usethis::use_dev_package('marcR', remote = 'github::MARC-KC/marcR')
usethis::use_pipe()
```






